---
title: "Mauricio Uriona Maldonado - CV"
author: Mauricio Uriona Maldonado
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
output:
  pagedown::html_resume:
    #css: ['dd_cv.css', 'resume1.css']
    css: ['custom_resume_mleary.css', 'styles_html_mleary.css', 'resume']
    #css: ['dd_cv_milz.css','custom_milz.css','resume']
    self_contained: false
knit: pagedown::chrome_print
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
library(fontawesome)
source("cv_printing_functions.r")
library(googlesheets4)
library(rorcid)
#devtools::install_github("hadley/emo")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1kMr3CCTRpn7tkGkcfm50V-NeJKNlaXmHznc-iWx09ts/edit#gid=917338460",  
  pdf_mode = params$pdf_mode
)

```

```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```

# Aside

```{r, eval=TRUE}
if(params$pdf_mode){
  cat("View this CV online with links at https://cv-muriona.netlify.app/")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/muriona/cv/blob/main/index.pdf)")
}
```

## Contact {#contact}

- Born and raised in La Paz, Bolivia `r emo::ji("bolivia")`

- Lives in Florianopolis, Brazil `r emo::ji("brazil")`

```{r message=FALSE, warning=FALSE}
library(lubridate)

dob <- ymd(19820425)
myage <- interval(dob,today())
myage <- myage %/% years(1)

```

- Age: *`r myage` years old*

```{r contactinfo}
#CV %>% print_contact_info()

glue::glue('
    - <i class="fa fa-envelope"></i> m.uriona@ufsc.br
    - <i class="fa fa-globe"></i> [-](http://www.sinergia.ufsc.br/eng-uriona) <i class="fa fa-github"></i> [-](https://github.com/muriona) <i class="fab fa-linkedin-in"></i> [-](https://www.linkedin.com/in/uriona/) <i class="fa fa-globe"></i> [-](https://www.orcid.org/0000-0002-1174-4828) <i class="fab fa-researchgate"></i> [-](https://www.researchgate.net/profile/Mauricio-Uriona-Maldonado-2)
  ')
```



## Language Skills {#skills}

```{r langskills}
CV %>% print_skill_bars()

```

## Specific Skills {#specskills}

```{r techskills}
CV %>% print_techskill_bars()
```

## Programming Skills {#techskills}

```{r otherskills}

glue::glue('
    - <i class="fa fa-laptop"></i> [Stella](http://www.iseesystems.com)
    
    - <i class="fa fa-laptop"></i> [Vensim](http://www.vensim.com)
    
    - <i class="fab fa-r-project"></i> [R](https://www.r-project.org/)
    
    - <i class="fab fa-python"></i> [Python](https://www.python.org/)
  ')

```


## Disclaimer {#disclaimer}

Made with [**pagedown**](https://github.com/rstudio/pagedown), an *R* package.

Last updated on `r format(Sys.Date(), "%d-%b-%Y")`.

# Main

## Mauricio Uriona Maldonado {#title}

```{r}
# Note the special double pipe so we modify the CV object in place
#CV %<>% print_text_block("intro") 

intro <- orcid_bio("0000-0002-1174-4828")
intro <- intro$`0000-0002-1174-4828`$content
as.character(intro)
```

## Education {data-icon="graduation-cap" data-concise="true"}

```{r}
CV %<>% print_section('education')
```

## Academic Experience {data-icon="chalkboard-teacher"}

```{r teaching}
CV %<>% print_section('teaching_positions')
```



## Visiting Positions {data-icon="globe"}

```{r}
CV %<>% print_section('research_positions')

#**Learning online from:**

#-   Datacamp
#-   Coursera
#-   EDx
#-   Linkedin Learning
#-   Tableau for Teaching

```

 
::: {.aside}


***Noteworthy International Collaborations***

- w/ Prof. Sara Grobbelaar `r emo::ji("south_africa")`
- w/ Prof. Peter Wells `r emo::ji("uk")`
- w/ Prof. Milton Herrera `r emo::ji("colombia")`
- w/ Prof. Minelle Silva `r emo::ji("france")`
- w/ Prof. Guillermo Davila `r emo::ji("peru")`

```{r eval=FALSE}
CV %<>% print_text_block('learning_experience_aside')
```
:::




## Industry Experience {data-icon="suitcase"}

```{r}
CV %<>% print_section('industry_positions')
```

<!-- These breaks just force a new page so section doesnt get cut off -->

```{css, echo=FALSE, eval=TRUE}
.extra-sidebar {
  top: 0;
  padding-top: 0;
}

.extra-sidebar h1 {
  display: none;
}

.extra-sidebar .level2:first-of-type {
  margin-top: 0;
}

# Second page sidebar {.aside .extra-sidebar}
```

\newpage

## Selected Publications {data-icon="book"}


```{r articles}
CV %<>% print_section('academic_articles')
```


```{r links}
CV %<>% print_links()
```



# Aside {.aside .extra-sidebar}

## Pub Record

-   **65** Journal Publications
-   **5** Books
-   **29** Book Chapters
-   **138** Conference Papers

See full details at the Brazilian Lattes online cv Platform [here](http://lattes.cnpq.br/6929645347412345)
