---
title: "Mauricio Uriona Maldonado - CV"
author: Mauricio Uriona Maldonado
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume1.css']
    self_contained: false
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
library(fontawesome)
source("cv_printing_functions.r")
library(googlesheets4)
library(rorcid)

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1kMr3CCTRpn7tkGkcfm50V-NeJKNlaXmHznc-iWx09ts/edit#gid=917338460",  
  pdf_mode = params$pdf_mode
)

```

```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```

# Aside

```{r, eval=TRUE}
if(params$pdf_mode){
  cat("View this CV online with links at https://cv-muriona.netlify.app/")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/muriona/cv/raw/master/muriona-cv.pdf)")
}
```

## Contact {#contact}

```{r eval = FALSE}
CV %>% print_contact_info()
```

-   `r fa("envelope", fill = "#254661",height = "20px")` [m.uriona at ufsc.br](mailto:m.uriona@ufsc.br)

-   `r fa("link", fill = "#254661",height = "20px")` [sinergia](http://www.sinergia.ufsc.br/eng-uriona)

-   `r fa("researchgate", fill = "#254661",height = "20px")` [researchgate](https://www.researchgate.net/profile/Mauricio-Uriona-Maldonado-2)

-   `r fa("linkedin", fill = "#254661",height = "20px")` [uriona](https://www.linkedin.com/in/uriona/)

-   `r fa("orcid", fill = "#254661", height = "20px")` [0000-0002-1174-4828](https://orcid.org/0000-0002-1174-4828)

## Language Skills {#skills}

```{r}
CV %>% print_skill_bars()
```

## Specific Skills {#specskills}

-   `r fa("laptop", fill = "#254661",height = "1em")` **Programming**: RStudio, System Dynamics (Stella and Vensim), Tableau
-   `r fa("lightbulb", fill = "#254661",height = "1em")` **Other**: data analysis, data visualization, machine learning

## Disclaimer {#disclaimer}

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r format(Sys.Date(), "%Y-%b-%d")`.

# Main

## Mauricio Uriona Maldonado {#title}

```{r}
# Note the special double pipe so we modify the CV object in place
#CV %<>% print_text_block("intro") 

intro <- orcid_bio("0000-0002-1174-4828")
intro <- intro$`0000-0002-1174-4828`$content
as.character(intro)
```

## Education {data-icon="graduation-cap" data-concise="true"}

```{r}
CV %<>% print_section('education')
```

## Teaching Experience {data-icon="chalkboard-teacher"}

```{r teaching}
CV %<>% print_section('teaching_positions')
```

## Training Abroad {data-icon="globe"}

```{r}
CV %<>% print_section('research_positions')
```

::: {.aside}
```{r eval=FALSE}
CV %<>% print_text_block('learning_experience_aside')
```
:::

## Distance Learning Education {.aside .extra-sidebar data-icon="school"}

-   Datacamp

-   Coursera

-   EDx

-   Linkedin Learning

-   Tableau for Teaching


## Industry Experience {data-icon="suitcase"}

```{r}
CV %<>% print_section('industry_positions')
```

<!-- These breaks just force a new page so section doesnt get cut off -->

```{css, echo=FALSE, eval=TRUE}
.extra-sidebar {
  top: 0;
  padding-top: 0;
}

.extra-sidebar h1 {
  display: none;
}

.extra-sidebar .level2:first-of-type {
  margin-top: 0;
}

# Second page sidebar {.aside .extra-sidebar}
```

\newpage

## Selected Publications {data-icon="book"}


```{r articles}
CV %<>% print_section('academic_articles')
```


```{r links}
CV %<>% print_links()
```



# Aside {.aside .extra-sidebar}

## Pub Record

-   **59** Journal Publications
-   **5** Books
-   **29** Book Chapters
-   **59** Journal Publications
-   **138** Conference Papers

See full details in the online cv [here](http://lattes.cnpq.br/6929645347412345)
