---
title: "Mauricio Uriona Maldonado - CV"
author: Mauricio Uriona Maldonado
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['custom_resume_mleary.css', 'styles_html_mleary.css', 'resume']
    self_contained: false
knit: pagedown::chrome_print
bibliography: bibliography.bib
cls: getLattes/apa-single-spaced.csl
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
library(fontawesome)
source("cv_printing_functions.r")
library(googlesheets4)
library(rorcid)
library(tidyverse)
library(gt)
library(glue)
library(kableExtra)
#devtools::install_github("hadley/emo")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1kMr3CCTRpn7tkGkcfm50V-NeJKNlaXmHznc-iWx09ts/edit#gid=917338460",  
  pdf_mode = params$pdf_mode
)

```

```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```

# Aside

```{r, eval=TRUE}
if(params$pdf_mode){
  cat("View this CV online with links at https://cv-muriona.netlify.app/")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/muriona/cv/blob/main/index.pdf)")
}
```

## Contact {#contact}

-   Born and raised in La Paz, Bolivia `r emo::ji("bolivia")`

-   Lives in Florianopolis, Brazil `r emo::ji("brazil")`

```{r message=FALSE, warning=FALSE}
library(lubridate)

dob <- ymd(19820425)
myage <- interval(dob,today())
myage <- myage %/% years(1)

```

```{r getlattes, echo=FALSE}

library(getLattes)
lattes <- xml2::read_xml("getLattes/6929645347412345.zip")
artigos <- getArtigosPublicados(lattes)
livros <- getCapitulosLivros(lattes)
congressos <- getLattes::getTrabalhosEmEventos(lattes)
orid <- getLattes::getOrientacoesDoutorado(lattes)
orim <- getLattes::getOrientacoesMestrado(lattes)
```

-   Age: *`r myage` years old*

```{r contactinfo}
#CV %>% print_contact_info()

glue::glue('
    - <i class="fa fa-envelope"></i> m.uriona@ufsc.br
    - <i class="fa fa-globe"></i> [-](https://sinergia.ufsc.br/project/uriona/) <i class="fa fa-github"></i> [-](https://github.com/muriona) <i class="fab fa-linkedin-in"></i> [-](https://www.linkedin.com/in/uriona/) <i class="fa-brands fa-orcid"></i> [-](https://www.orcid.org/0000-0002-1174-4828) <i class="fab fa-researchgate"></i> [-](https://www.researchgate.net/profile/Mauricio-Uriona-Maldonado-2)
  ')
```

## Language Skills {#skills}

```{r langskills}
CV %>% print_skill_bars()

```

## Specific Skills {#specskills}

```{r techskills}
CV %>% print_techskill_bars()
```

## Modelling Skills {#techskills}

```{r otherskills}

glue::glue('
    - <i class="fa fa-laptop"></i> [Stella](http://www.iseesystems.com)
    
    - <i class="fa fa-laptop"></i> [Vensim](http://www.vensim.com)
    
    - <i class="fa fa-laptop"></i> [Anylogic](http://www.anylogic.com)
    
    - <i class="fab fa-r-project"></i> [R](https://www.r-project.org/)
    
    - <i class="fab fa-python"></i> [Python](https://www.python.org/)
  ')

```

## Disclaimer {#disclaimer}

Made with [**pagedown**](https://github.com/rstudio/pagedown), an *R* package.

Last updated on `r format(Sys.Date(), "%d-%b-%Y")`.

# Main

## Mauricio Uriona Maldonado {#title}

```{r}
# Note the special double pipe so we modify the CV object in place
#CV %<>% print_text_block("intro") 

intro <- orcid_bio("0000-0002-1174-4828")
intro <- intro$`0000-0002-1174-4828`$content

glue::glue('{intro}')
```

## Education {data-icon="graduation-cap" data-concise="true"}

```{r}
CV %<>% print_section('education')
```

## Academic Experience {data-icon="chalkboard-teacher"}

```{r teaching}
CV %<>% print_section('teaching_positions')
```

## Visiting Positions {data-icon="globe"}

```{r}
CV %<>% print_section('research_positions')

#**Learning online from:**

#-   Datacamp
#-   Coursera
#-   EDx
#-   Linkedin Learning
#-   Tableau for Teaching

```

::: aside
***Industry Experience***

-   Consultant in Innovation Management (FIESC) - 2012-2013
-   Business Analyst (Dinamica Software) - 2005-2008

***Noteworthy International Collaborations***

-   w/ Prof. Sara Grobbelaar (Stellenbosch Univ) `r emo::ji("south_africa")`
-   w/ Prof. Rainer Walz (Fraunhofer ISI) `r emo::ji("germany")`
-   w/ Prof. Milton Herrera (Univ Militar Nueva Granada)`r emo::ji("colombia")`
-   w/ Prof. Minelle Silva (La Rochele Business School)`r emo::ji("france")`
-   w/ Prof. Guillermo Davila (Univ de Lima) `r emo::ji("peru")`
-   w/ Prof. Peter Wells (Cardiff Univ)`r emo::ji("uk")`

```{r eval=FALSE}
CV %<>% print_text_block('learning_experience_aside')
```
:::

## Funding and Grants {data-icon="dollar-sign"}

```{r}
CV %<>% print_section('industry_positions')

#data-icon="money-check-dollar"


```

```{css, echo=FALSE, eval=FALSE}


.extra-sidebar {
  top: 0;
  padding-top: 0;
}

.extra-sidebar h1 {
  display: none;
}

.extra-sidebar .level2:first-of-type {
  margin-top: 0;
}

# Second page sidebar {.aside .extra-sidebar}
#<!-- These breaks just force a new page so section doesnt get cut off -->
```


## Selected Publications {data-icon="book"}

```{r articles, eval=TRUE}
#CV %<>% print_section('academic_articles')

artigos %>% 
  mutate(ano = as.numeric(ano_do_artigo)) %>% 
  select(ano, titulo_do_artigo_ingles, titulo_do_periodico_ou_revista,
         doi) %>% 
  mutate(doi = sprintf('<p><a href = "%s">%s</a>', doi,doi),
         doi = map(doi, gt::html),
         titulo_do_artigo_ingles = ifelse(is.na(titulo_do_artigo_ingles),titulo_do_artigo,                                          titulo_do_artigo_ingles)) %>% 
  arrange(desc(ano)) %>% 
  head(20) %>% 
  gt::gt() %>% 
  tab_options(table.font.size = pct(80)) %>% 
  cols_label(
    titulo_do_artigo_ingles = "Title",
    ano = "Year",
    titulo_do_periodico_ou_revista = "Journal"
  )%>% 
  tab_header(
    title = "Most Recent Publications"
  )
```

```{r message=FALSE, warning=FALSE}
library(bib2df)
scopus <- bib2df("getLattes/scopus.bib") %>% 
  separate(NOTE, into = c("note","citations"), sep = ":") %>% 
  separate(citations, into = c("citations","open"), sep = ";") %>% 
  mutate(citations = as.numeric(citations),
         YEAR = as.numeric(YEAR),
         DOI = sprintf('<p><a href = "%s">%s</a>', DOI,DOI),
         DOI = map(DOI, gt::html))

scopus %>% 
  filter(CATEGORY == "ARTICLE") %>% 
  filter(citations > 7) %>% 
  arrange(desc(citations)) %>% 
  select(YEAR, TITLE, JOURNAL, DOI, citations) %>% 
  head(10) %>% 
  gt() %>% 
  tab_options(table.font.size = pct(80)) %>% 
  cols_label(
    TITLE = "Title",
    YEAR = "Year",
    JOURNAL = "Journal"
  ) %>% 
  tab_header(
    title = "Top-10 Highly Cited Publications"
  )
  
```


```{r eval=FALSE}
artigos %>% 
  mutate(ano = as.numeric(ano_do_artigo)) %>% 
  arrange(desc(ano)) %>% 
  mutate(titulo_do_artigo_ingles =
           ifelse(is.na(titulo_do_artigo_ingles),
                  titulo_do_artigo,           
                  titulo_do_artigo_ingles),
         home_page_do_trabalho=
           ifelse(is.na(home_page_do_trabalho), doi,
                  home_page_do_trabalho)) %>%
  head(15) %>% 
  select(ano, titulo_do_artigo_ingles, titulo_do_periodico_ou_revista) %>% 
  kbl(col.names = c("Year", "Title","Journal"),
      align = c("c","l","l","l"))# %>%
 # kable_styling(full_width = F) %>%
 # column_spec(1, width = "15em", bold = T, border_right = T) %>%
#  column_spec(2, width = "35em", bold = F, border_right = T) %>%
 # column_spec(3, width = "30em", bold = F, border_right = T) %>%
  ##column_spec(4, width = "10em", bold = F, border_right = T) %>%
  #row_spec(row = 0, color = "white", background = "dodgerblue")
##  column_spec(2, width = "30em", background = "yellow")
  
```



```{r links, eval=FALSE}
CV %<>% print_links()
```

# Aside {.aside .extra-sidebar}

## Pub Record

-   **`r nrow(artigos)`** Journal Publications
-   **5** Books
-   **`r nrow(livros)`** Book Chapters
-   **`r nrow(congressos)`** Conference Papers

## Supervisions

-   **`r nrow(orid)`** Completed PhD Supervisions
-   **`r nrow(orim)`** Completed MSc Supervisions

See full details at the Brazilian Lattes online cv Platform [here](http://lattes.cnpq.br/6929645347412345)

